{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-12-08 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

    We warn the readers about the followings: 
        \item The proofs in HongZhou Lin's original paper of Universal Catalyst is depressingly long and complicated. It is a result of using the constructive approach of Nesterov's estimating sequence. 
        \item Controlling the errors of inexact proximal point evaluations is context specific. Lin hinted at ways to track the errors such as using duality and non-negativity assumption of the objective. He illustrated the use of the meta acceleration on their own method called: ``Accelerated MISO-Prox", in general there is not a universal solution. 
        \item We will provide proofs to clarify some of their proofs and compare with existing proofs and drawing references in the literatures in the appendix. 

@@

    Their algorithm is almost exactly the same as Nesterov's 2.2.20 \cite{nesterov_lectures_2018} which we stated in the definition below: 

@@

    For theoretical interests, there is a major difference between Lin's approach and Guler's approach. 
    Lin didn't formulate any of the intractable quantities in the definitions for his Nesterov's estimating sequence $\phi_k$. 
    One major innovation is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015} which is stated below. 
    The lemma allows the analysis of Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.

>>>>

@@

    The definition below states Lin's accelerated inexact proximal point method. 
    Observe that it's similar to Nesterov's 2.2.20 \cite{nesterov_lectures_2018}. 

@@

    For theoretical interests, there is a major difference between Lin's approach and Guler's approach. 
    Lin didn't formulate any of the intractable quantities in the definitions for his Nesterov's estimating sequence $\phi_k$. 
    One major innovation is Lemma A.7 in Lin's 2015 paper \cite{lin_universal_2015} which is stated below. 
    The lemma allows the analysis of Nesterov's estimating sequence to be carried through without using intractable quantities: $\mathcal M^{\kappa^{-1}}(\mathcal J_{k^{-1}}y_{k - 1}, y_{k - 1}), \mathcal J_{\kappa^{-1}}y_{k - 1}$.
